% Raphael Walker Resume
\documentclass[12pt,letterpaper]{article}
\usepackage{geometry}
\geometry{
	letterpaper,
	top=0.6in,
	bottom=0.4in,
	left=0.5in,
	right=0.5in
	}
\usepackage{mdwlist}
% Fonts
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[babel=true]{microtype}

\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{multicol}
% Hyperlink setup
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newenvironment{explist}
{\begin{itemize}[label=\textbf{--},itemsep=1pt,topsep=0pt,partopsep=0pt,parsep=0pt]}
{\end{itemize}}

\begin{document}

\begin{center}
	{\LARGE{\textbf{Rafie Walker}}}\\[0.05in]

	\begin{tabular}{r @{\hskip 0.1in}|@{\hskip 0.1in} l}
		(510) 847-3889 & rw8103@bard.edu \\
		 \href{https://github.com/Slickytail}{\faGithub.com/Slickytail} &
		 \href{https://linkedin.com/in/raphael-walker}{\faLinkedinSquare.com/in/Raphael-Walker}
	\end{tabular}
\end{center}
\hrule \vspace{-0.5em}

\section*{Education} \vspace{-0.5em}
\begin{itemize}[label=,itemsep=0pt]
	\item
	\textbf{Bard College} \textit{Annandale-On-Hudson, New York} \hfill Expected May 2021\\
    \textit{Bachelor of Arts, Mathematics Major}\hfill \textit{GPA 4.0}
	\item
	\textbf{Bard College at Simon's Rock} \textit{Great Barrington, Massachusetts} \hfill May 2019\\
	\textit{Associate of Arts} \hfill \textit{GPA 3.9}\\
	Mathematics and Computer Science Tutor
\end{itemize}
\vspace{-2em}

\section*{Work Experience} \vspace{-0.5em}
\begin{itemize}[label=,itemsep=0pt]
    \item
    \textbf{Bard Summer Research Intensive} \hfill Summer 2020\\
    \textit{Research Assistant, Mathematics}
    \begin{explist}
        \item Investigated the size of maximal generalized caps in finite affine spaces.
        \item Introduced other students in the research group to the material and supported their exploration of related problems.
    \end{explist}
	\item 
	\textbf{Invisible College} \hfill Summers 2019, 2020\\
	\textit{Research Assistant}
	\begin{explist}
		\item Designed and developed a set of decentralized synchronization protocols and algorithms.
		\item Co-authored IETF draft for universal synchronization protocol.
		\item Created Javascript and NodeJS tools to analyze and debug synchronization algorithms, including a universal protocol translation demo and a peer-to-peer sync visualization.
        \item Contributed to client and server code for the \underline{\href{https://github.com/braid-work/braidjs}{BraidJS}} library.
	\end{explist}

	\item
	\textbf{Speakeasy Digital Media} \hfill August 2018---February 2019\\
	\textit{Web Developer}
	\begin{explist}
		\item Created and modified WordPress PHP templates for company blogs.
		\item Improved page load times by up to ten times by optimization on both front-end page loading and back-end content generation.
	\end{explist}
	
	\item
	\textbf{Storefront Political} \hfill May 2018---August 2018\\
	\textit{Data Science Intern}
	\begin{explist}
		\item Analyzed pre-electoral polls, including weighting, cross-tabulating, raking, and cleaning.
		\item Created R and Python scripts to automate common tasks such as matching ZIP codes to voting districts and visualizing survey results.
		\item Designed and implemented a webapp for interactive visualization of survey results.
		\item Managed large PostgreSQL databases containing voter information.
	\end{explist}

	\item
    \textbf{Qu-Swap (Hackathon project)} \hfill December 2018---February 2019\\
	\textit{Front-end Developer}
	\begin{explist}
		\item Designed and implemented UI (JS, CSS, HTML, Bootstrap) and UX for a textbook-swap website.
	\end{explist}
	
    \item
	\textbf{Omnisparx} \hfill November 2017---April 2018\\
	\textit{Intern}
	\begin{explist}
		\item Researched and reported on the state of blockchain technology to educate app users and inform development for blockchain start-up.
	\end{explist}
\end{itemize}

\end{document}
